\documentclass[10pt]{extarticle}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{color}
\usepackage[a4paper, margin=1cm]{geometry}
\usepackage{tgcursor}
\newcommand\userinput[1]{\textbf{#1}}
%\sloppy
\setlength{\parindent}{0pt}

\begin{document}

{\Large \textbf{GroundControllerInputs}}
 \begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{UTC_Time}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{DF_telemetry}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{GCC_ControlFlags}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{systemState}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{trueAirspeed}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.altitude
        logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{altitude.value}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{velocityPlaneGround}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{distancePlaneGround}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.accelerationPlaneGround
        logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{accelerationPlaneGround.value}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.controlDemand
        logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetry.\textbf{controlDemand.value}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{telemetryUTC_Time}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{DF_GCS_GCC_StateCommand}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.GCS_GCC_StateCommand
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{GCS_GCC_StateCommand.UTC_Time}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{GCS_GCC_StateCommand.commandFlag}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{GCS_GCC_StateCommand.data}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{DF_GCS_GCC_Command}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.GCS_GCC_Command
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{GCS_GCC_Command.UTC_Time}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{GCS_GCC_Command.commandID}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{GCS_GCC_Command.data}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{DF_winchData}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.winchData
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.winchID}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.state}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.ecode}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.alarm0}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.alarm1}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.alarm2}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.speed_demand}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.length_total}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.length_on_drum}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.tether_speed}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchData.tether_tension}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{DF_winchMotorData}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.winchMotorData
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.alarms}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.dc_voltage}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.stator_freq}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.rms_current}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.active_power}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.active_current}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.torque}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.actual_freq}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.output_rms_voltage}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{winchMotorData.error_count}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{DF_telemetrySync}

logData_FCC114_1.\underline{GroundControllerInputs}.packetData.telemetrySync
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{telemetrySync.systemState}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{telemetrySync.numberOfPackets}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{telemetrySync.packetIndex}
    logData_FCC114_1.\underline{GroundControllerInputs}.packetData.\textbf{telemetrySync.syncData}
\end{Verbatim}
\newpage
{\Large \textbf{NavigationData}}
 \begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.NavigationData.packetData.\textbf{navMode}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{UTC_Time}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{positionLLH}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{positionNED}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{velocityNED}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{rollPitchYaw}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{bodyRate}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{navAccel}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{bodyAccel}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{inertialAccel}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{windSpeed}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{gravityNED}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{heightAboveGround}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{heightAboveGroundRate}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{terrainPitchRoll}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{angleOfAttackOffset}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{sideSlipOffset}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{cosMatBodyToNav}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{pressureAltitudeOffset}

logData_FCC114_1.\underline{NavigationData}.packetData.\textbf{angularAccel}
\end{Verbatim}
\newpage
{\Large \textbf{ProcessedSensorData}}
\begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{propulsionBatteryRemaining}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{airDataInterfaceHealth}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{trueAirspeed}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{equivalentAirspeed}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{dynamicPressure}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{inverseDynamicPressure}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{angleOfAttackValid}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{angleOfAttack}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{sideSlipValid}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{sideSlip}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{pressureAltitude}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{cableT}ension

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{autopilotVoltage}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoVoltage1}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoVoltage2}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{PPS_Pulse}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{highRangeAccelerometer}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{engineVoltage}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{engineCurrent}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{engineConsumption}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{engineDischarge}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{engineSwitch}

logData_FCC114_1.\underline{ProcessedSensorData}.packetData.servoDeflections
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.stbdFlap}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_portAileron}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.portAileron}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_stbdAileron}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.stbdAileron}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_portElevator}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.portElevator}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_stbdElevator}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.stbdElevator}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_rudder}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.rudder}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_portFlap}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.portFlap}
    logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{servoDeflections.DF_stbdFlap}
	
logData_FCC114_1.\underline{ProcessedSensorData}.packetData.\textbf{CPU_Temperature}
\end{Verbatim}
\newpage
{\Large \textbf{ServoDemandFCC}}
\begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.ServoDemandFCC.packetData.demands
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.flags}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.throttle}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.port_aileron}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.stbd_aileron}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.port_flap}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.stbd_flap}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.rudder}
    logData_FCC114_1.\underline{ServoDemandFCC}.packetData.\textbf{demands.elevator}
\end{Verbatim}
\vspace{1cm}
{\Large \textbf{SystemState}}
\begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.\underline{SystemState}.packetData.\textbf{currentState}

logData_FCC114_1.\underline{SystemState}.packetData.\textbf{currentSubState}

logData_FCC114_1.\underline{SystemState}.packetData.\textbf{previousState}

logData_FCC114_1.\underline{SystemState}.packetData.\textbf{previousSubState}

logData_FCC114_1.\underline{SystemState}.packetData.\textbf{transitionTaken}

logData_FCC114_1.\underline{SystemState}.packetData.\textbf{stateFlags}

logData_FCC114_1.\underline{SystemState}.packetData.\textbf{commandFlags}
\end{Verbatim}
\vspace{1cm}
{\Large \textbf{WinchData}}
\begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.\underline{WinchData}.packetData.\textbf{winchID}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{state}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{ecode}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{alarm0}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{alarm1}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{alarm2}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{speed_demand}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{length_total}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{length_on_drum}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{tether_speed}

logData_FCC114_1.\underline{WinchData}.packetData.\textbf{tether_tension}
\end{Verbatim}
\newpage
{\Large \textbf{WinchMotorData}}
\begin{Verbatim}[baselinestretch=.9,commandchars=\\\{\}]
logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{alarms}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{dc_voltage}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{stator_freq}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{rms_current}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{active_power}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{active_current}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{torque}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{actual_freq}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{output_rms_voltage}

logData_FCC114_1.\underline{WinchMotorData}.packetData.\textbf{error_count}
\end{Verbatim}




\end{document}

